%-----------------------------------------------------------------------------%
\chapter*{\MakeUppercase{\textit{\judulInggris}}}
%-----------------------------------------------------------------------------%
\singlespacing
\begin{center}
    
    \vspace{-4em}
    
    \penulis
    
	\bigskip
    
    \textit{\textbf{ABSTRACT}}
    
\end{center}

% \chapter*{Abstrak}

\vspace*{0.2cm}
{
	\setlength{\parindent}{0pt}

	\bigskip
	\bigskip

    This report describes the development of the Nine to Six (NTS) human resource information system at PT Visi Karya Nusantara, a technology information consulting company focused on innovative digital solutions. The digitalization of human resource management has become a critical necessity to improve operational efficiency, payroll accuracy, and regulatory compliance. Research demonstrates that the integration of modules such as Contract Management, Overtime Management, and Payslip significantly reduces manual errors and enhances data transparency. This project was designed to develop an integrated system that connects static data (employee contracts), transactional data (attendance and overtime), and compensation finalization processes (payslip) within a single cloud-based platform. Using the PERN Stack (PostgreSQL, Express.js, React.js, Node.js), the system was developed with Agile methodology during the internship period from August 4, 2025 to January 4, 2026. The development outcomes include the implementation of Contract Management module, Payroll with automated components, Overtime Management, CSV-based On Boarding, and Payslip integrated with the Daily Attendance system. This system is expected to enhance HR efficiency, ensure accurate compensation calculations, and provide full transparency to employees through self-service access.
	
	\bigskip
 
% keywords in alphabetical order
% 3 – 5 keywords
	\textbf{Keywords}: \textit{Backend development, Express, Human resource information system, On boarding, Payroll.}	
}

\onehalfspacing